Pre/Post-Trikafta

### 2022-01-19 Christine Chan/Pre-post Trikafta/pre_post_trikafta.Rmd
Update pre_post_trikafta.Rmd
nicer printing

```{r setup, include=FALSE}
library(arsenal)
library(tidyverse)
library(lubridate)
library(readxl)
library(PAutilities)
library(AGD)
library(rspiro)
library(anthro)
library(knitr)
knitr::opts_chunk$set(echo = FALSE)
knitr::opts_knit$set(root.dir = "/Volumes/PEDS/RI Biostatistics Core/Shared/Shared Projects/Vigers/CF/Christine Chan/Prepost Triakfta")
```

```{r}
############pre/post trikaftka
# c. chan
##############################
library(dplyr)
setwd("S:/PEDS/RI Biostatistics Core/Shared/Shared Projects/Meier/CF/2020.02.09 - Prepost Triakfta/")

#cgm data
# cgm_c <- read.csv("REDCap Upload.csv")
cgm_c <- read.csv("Data From CHCO/REDCap Upload_chco.csv")
cgm_c$date_cgm <- as.Date(cgm_c$date_cgm_placement, "%Y-%m-%d")

cgm_m <- read.csv("Data From Montana/CGM_Montana/REDCap Upload_mt.csv")
cgm_m$date_cgm <- as.Date(cgm_m$date_cgm_placement, "%m/%d/%Y")

cgm_w <- read.csv("Data From Washington/REDCap Upload_Washington.csv")
cgm_w$date_cgm <- as.Date(cgm_w$date_cgm_placement, "%Y-%m-%d")

@@

`%!in%` = Negate(`%in%`)
reg0 <- read.csv("Data From CHCO/Registry/Copy of Earliest Trikafta Dates in Registry_updated 2.2.21 cc modified_cfrdyn.csv")
#need to get rid of those two
reg <- subset(reg0, reg0$MRN %!in% c("1714343", "787372") )

@@

a1c <- read.csv("Data From CHCO/Copy of A1C and OGTTs Before and After Trikafta_cc modified 8.25.20.csv")

weight <- read.csv("Data From CHCO/Registry/weightdata.csv")

@@

reg_montana <- read.csv("S:/PEDS/RI Biostatistics Core/Shared/Shared Projects/Meier/CF/2020.02.09 - Prepost Triakfta/Data From Montana/Copy of Paper patient population glycemic (+hofer).csv")

demo_adult <- read.csv("S:/PEDS/RI Biostatistics Core/Shared/Shared Projects/Meier/CF/2020.02.09 - Prepost Triakfta/Data From Montana/demo_adults.csv")
demo_kids <- read.csv("S:/PEDS/RI Biostatistics Core/Shared/Shared Projects/Meier/CF/2020.02.09 - Prepost Triakfta/Data From Montana/demo_kids.csv")

@@

pft_adult <- read.csv("S:/PEDS/RI Biostatistics Core/Shared/Shared Projects/Meier/CF/2020.02.09 - Prepost Triakfta/Data From Montana/Copy of PFTs growth adult (+hofer).csv")
pft_kids <- read.csv("S:/PEDS/RI Biostatistics Core/Shared/Shared Projects/Meier/CF/2020.02.09 - Prepost Triakfta/Data From Montana/PFTs kids.csv")

@@

pft_montana_5$BMI.Percentile

@@

gt_adult <- read.csv("S:/PEDS/RI Biostatistics Core/Shared/Shared Projects/Meier/CF/2020.02.09 - Prepost Triakfta/Data From Montana/gtubes_adult.csv")
gt_kids <- read.csv("S:/PEDS/RI Biostatistics Core/Shared/Shared Projects/Meier/CF/2020.02.09 - Prepost Triakfta/Data From Montana/GT users kids.csv")

@@

is_adult <- read.csv("S:/PEDS/RI Biostatistics Core/Shared/Shared Projects/Meier/CF/2020.02.09 - Prepost Triakfta/Data From Montana/pancreatic insufficient adult.csv")
is_kids <- read.csv("S:/PEDS/RI Biostatistics Core/Shared/Shared Projects/Meier/CF/2020.02.09 - Prepost Triakfta/Data From Montana/pancreatic insufficient kids.csv")

@@

g_adult <- read.csv("S:/PEDS/RI Biostatistics Core/Shared/Shared Projects/Meier/CF/2020.02.09 - Prepost Triakfta/Data From Montana/genotypes_adult.csv")
g_kids <- read.csv("S:/PEDS/RI Biostatistics Core/Shared/Shared Projects/Meier/CF/2020.02.09 - Prepost Triakfta/Data From Montana/genotypes kids.csv")[,1:3]

@@

reg_washington <- read.csv("Data From Washington/Copy of CFRD and trikafta Trikafta_on_Annual_Review-13-Apr-2021-0815.csv")
reg_wash <- read.csv("Data From Washington/Copy of CFRD and trikafta Trikafta_on_Annual_Review-13-Apr-2021-0815.csv")

@@

#aic 
a1c_wash <- read.csv("Data From Washington/A1C_and_OGTT.csv")

@@

#bmi
bmi_wash <- read.csv("Data From Washington/BMIandWeight.csv")
bmi_wash1 <- merge(bmi_wash, analytic_wash, by = "CFF.ID")
bmi_wash1$Date <- as.Date(bmi_wash1$Date.of.Encounter.x,  "%m/%d/%Y")
bmi_wash1$diff <-as.numeric(bmi_wash1$Date - bmi_wash1$trik)

@@

#sex
demo_wash <- read.csv("Data From Washington/Demographics.csv")

@@

#Insufficent
is_wash <- read.csv("Data From Washington/Pancreatic_Insufficient.csv")

@@

gt_wash <- read.csv("Data From Washington/G-tube.csv")

@@

geno_wash <- read.csv("Data From Washington/Genotypes.csv")

@@

pfts_wash <- read.csv("Data From Washington/PFTs.csv")

@@

uofm <- read.csv("Data from UofM/Moheet_Pre_Post_Trikafta_FinalData_20210914.csv")
analytic_uofm <- subset(uofm, uofm$CFRD.Status == "CFRD with or without fasting hyperglycemia")
analytic_uofm$age <- analytic_uofm$age.at.Trikafta.start

@@

analytic_uofm2$BMI.Value <- analytic_uofm2$bmi
analytic_uofm2$age_category
analytic_uofm2_2 <- subset(analytic_uofm2, analytic_uofm2$Encounter....of.Days.POST.Trikafta.start <= 365 &
                             analytic_uofm2$Encounter....of.Days.PRE.Trikafta.Start <= 365)

@@

a1c_wash2

reg_montana2

@@

mycontrols  <- tableby.control(test=FALSE, total=FALSE,
                               numeric.test="kwt", cat.test="chisq",
                               numeric.stats=c("N", "median", "q1q3"),
                               cat.stats=c("countpct"),
                               stats.labels=list(N='Count', median='Median', q1q3='Q1,Q3'))

tab2 <- tableby(prepost ~ n, control=mycontrols, data=a1c7)

@@

#number of values pre/post
#row 1 in table 2
a <- merge(before, after, by = "CFF.ID", all.y = T)
wilcox.test(a$pre,a$post, paired = T)

@@

summary(before_max$time)
sd(before_max$time)

@@

summary(after_max$time)
sd(after_max$time)

#test this
t.test(before_max$time,after_max$time)

time <- merge(before_max,after_max,by='CFF.ID',all.y=T)
summary(time$time.x)
sd(time$time.x, na.rm=T)
summary(time[!is.na(time$time.x),]$time.y)
sd(time[!is.na(time$time.x),]$time.y, na.rm=T)
t.test(time$time.x,time$time.y, paired = T)

@@

t.test(as.numeric(time$Hgb.A1C.x),as.numeric(time$Hgb.A1C.y), paired = T)

summary(as.numeric(time$Hgb.A1C.x))
sd(as.numeric(time$Hgb.A1C.x), na.rm=T)

summary(as.numeric(time$Hgb.A1C.y))
sd(as.numeric(time$Hgb.A1C.y),na.rm=T)

@@

time$diff_a1c <- as.numeric(time$Hgb.A1C.x) - as.numeric(time$Hgb.A1C.y)
summary(time[time$Hgb.A1C.x < 6.5, ]$diff_a1c)

t.test(time[time$Hgb.A1C.x < 6.5, ]$diff_a1c, mu=0)

@@

wilcox.test(as.numeric(time2$Hgb.A1C.x), as.numeric(time2$Hgb.A1C.y), paired = T)

@@

summary(ins7[ins7$prepost == "Post",]$Long.acting.or.total.basal.daily.dose..units.)

@@

wilcox.test(ins8$Long.acting.or.total.basal.daily.dose..units..x, ins8$Long.acting.or.total.basal.daily.dose..units..y, paired = T)

@@

tab2 <- tableby(time~Weight+ bmiz + ppFEV1+ppFVC, data=timing)

timing2 <- merge(weigh_before1,weigh_after1, by = "MRN", all.y=T)
wilcox.test(timing2$ppFEV1.x,timing2$ppFEV1.y, paired=T)

wilcox.test(timing2$ppFVC.x,timing2$ppFVC.y, paired=T)

@@

tab2b<- tableby(prepost~ppFVC + ppFEV1 + bmipct + Weight + BMI.Value, data=bmidat4[bmidat4$CFF.ID %in% time[!is.na(time$prepost.x),]$CFF.ID,])

tab2b<- tableby(prepost~ppFVC + ppFEV1 + bmipct + Weight + BMI.Value, data=bmidat4[bmidat4$CFF.ID %in% a$CFF.ID,])

@@

t.test(as.numeric(bmidat4$ppFVC.x),as.numeric(bmidat4$ppFVC.y), paired = T)
t.test(bmidat4$ppFEV1.x,bmidat4$ppFEV1.y, paired = T)
t.test(bmidat4$bmipct.x,bmidat4$bmipct.y , paired = T)
t.test(as.numeric(bmidat4$Weight.x),as.numeric(bmidat4$Weight.y) , paired = T)
t.test(as.numeric(bmidat4$BMI.Value.x),as.numeric(bmidat4$BMI.Value.y) , paired = T)

@@

View(cgm0[,c("subject_id", "ID", "time")])

@@

View(cgm0_time[,c("date_cgm", "trik", "diff", "ID", "time")])

@@

tab3 <- tableby(time~ average_sensor
+ min_sensor
+ max_sensor
+ percent_time_over_120
+ percent_time_over_140
+ percent_time_over_200
+ avg_excur_over_140_per_day
+ avg_excur_over_200_per_day
+ percent_time_under_60
+ percent_time_under_70
+ average_auc_per_day
+ standard_deviation
+ r_mage, data=cgm0_small, control=mycontrols)

tab3 <- tableby(~average_sensor
                + min_sensor
                + max_sensor
                + percent_time_over_120
                + percent_time_over_140
                + percent_time_over_200
                + avg_excur_over_140_per_day
                + avg_excur_over_200_per_day
                + percent_time_under_60
                + percent_time_under_70
                + average_auc_per_day
                + standard_deviation
                + r_mage, data=cgm0[cgm0$time == "post",]
, control=mycontrols)

@@

wilcox.test(as.numeric(cgm0_time$diff )~cgm0_time$time, paired=T)
wilcox.test(temp$average_sensor.x ,temp$average_sensor.y, paired=T)
wilcox.test(temp$min_sensor.x   ,temp$min_sensor.y, paired=T)
wilcox.test(temp$max_sensor.x   ,temp$max_sensor.y, paired=T)
wilcox.test(temp$percent_time_over_120.x   ,temp$percent_time_over_120.y, paired=T)
wilcox.test(temp$percent_time_over_140.x   ,temp$percent_time_over_140.y, paired=T)
wilcox.test(temp$percent_time_over_200.x   ,temp$percent_time_over_200.y, paired=T)
wilcox.test(temp$avg_excur_over_140_per_day.x   ,temp$avg_excur_over_140_per_day.y, paired=T)
wilcox.test(temp$avg_excur_over_200_per_day.x   ,temp$avg_excur_over_200_per_day.y, paired=T)
wilcox.test(temp$percent_time_under_60.x   ,temp$percent_time_under_60.y, paired=T)
wilcox.test(temp$percent_time_under_70.x   ,temp$percent_time_under_70.y, paired=T)
wilcox.test(temp$average_auc_per_day.x   ,temp$average_auc_per_day.y, paired=T)
wilcox.test(temp$standard_deviation.x   ,temp$standard_deviation.y, paired=T)
wilcox.test(temp$r_mage.x   ,temp$r_mage.y, paired=T)

wilcox.test(cgm0_small$average_sensor~cgm0_small$time, paired=T)

@@

tab1 <- tableby(~age+bmipct + Weight + Sex + ppFEV1 + ppFVC  +
                  G.tube.in.past.12.months + Pancreatic.Status +
                  genoRisk + location+BMI.Value + age_category, 
                data=analytic_cm[analytic_cm$CFF.ID %in% cgm0_small$ID,])
```

>>>>

```{r setup, include=FALSE}
library(arsenal)
library(tidyverse)
library(lubridate)
library(readxl)
library(PAutilities)
library(AGD)
library(rspiro)
library(anthro)
library(knitr)
knitr::opts_chunk$set(echo = FALSE)
knitr::opts_knit$set(root.dir = "/Volumes/PEDS/RI Biostatistics Core/Shared/Shared Projects/Vigers/CF/Christine Chan/Prepost Triakfta/Data_Raw")
```

```{r warning=FALSE,results='asis'}
############pre/post trikaftka
# c. chan
##############################

#cgm data
# cgm_c <- read.csv("REDCap Upload.csv")
cgm_c <- read.csv("./Data From CHCO/REDCap Upload_chco.csv")
cgm_c$date_cgm <- as.Date(cgm_c$date_cgm_placement, "%Y-%m-%d")

cgm_m <- read.csv("./Data From Montana/CGM_Montana/REDCap Upload_mt.csv")
cgm_m$date_cgm <- as.Date(cgm_m$date_cgm_placement, "%m/%d/%Y")

cgm_w <- read.csv("./Data From Washington/REDCap Upload_Washington.csv")
cgm_w$date_cgm <- as.Date(cgm_w$date_cgm_placement, "%Y-%m-%d")

@@

`%!in%` = Negate(`%in%`)
reg0 <- read.csv("./Data From CHCO/Registry/Copy of Earliest Trikafta Dates in Registry_updated 2.2.21 cc modified_cfrdyn.csv")
#need to get rid of those two
reg <- subset(reg0, reg0$MRN %!in% c("1714343", "787372") )

@@

a1c <- read.csv("./Data From CHCO/Copy of A1C and OGTTs Before and After Trikafta_cc modified 8.25.20.csv")

weight <- read.csv("./Data From CHCO/Registry/weightdata.csv")

@@

reg_montana <- read.csv("./Data From Montana/Copy of Paper patient population glycemic (+hofer).csv")

demo_adult <- read.csv("./Data From Montana/demo_adults.csv")
demo_kids <- read.csv("./Data From Montana/demo_kids.csv")

@@

pft_adult <- read.csv("./Data From Montana/Copy of PFTs growth adult (+hofer).csv")
pft_kids <- read.csv("./Data From Montana/PFTs kids.csv")

@@

@@

gt_adult <- read.csv("./Data From Montana/gtubes_adult.csv")
gt_kids <- read.csv("./Data From Montana/GT users kids.csv")

@@

is_adult <- read.csv("./Data From Montana/pancreatic insufficient adult.csv")
is_kids <- read.csv("./Data From Montana/pancreatic insufficient kids.csv")

@@

g_adult <- read.csv("./Data From Montana/genotypes_adult.csv")
g_kids <- read.csv("./Data From Montana/genotypes kids.csv")[,1:3]

@@

reg_washington <- read.csv("./Data From Washington/Copy of CFRD and trikafta Trikafta_on_Annual_Review-13-Apr-2021-0815.csv")
reg_wash <- read.csv("./Data From Washington/Copy of CFRD and trikafta Trikafta_on_Annual_Review-13-Apr-2021-0815.csv")

@@

#aic 
a1c_wash <- read.csv("./Data From Washington/A1C_and_OGTT.csv")

@@

#bmi
bmi_wash <- read.csv("./Data From Washington/BMIandWeight.csv")
bmi_wash1 <- merge(bmi_wash, analytic_wash, by = "CFF.ID")
bmi_wash1$Date <- as.Date(bmi_wash1$Date.of.Encounter.x,  "%m/%d/%Y")
bmi_wash1$diff <-as.numeric(bmi_wash1$Date - bmi_wash1$trik)

@@

#sex
demo_wash <- read.csv("./Data From Washington/Demographics.csv")

@@

#Insufficent
is_wash <- read.csv("./Data From Washington/Pancreatic_Insufficient.csv")

@@

gt_wash <- read.csv("./Data From Washington/G-tube.csv")

@@

geno_wash <- read.csv("./Data From Washington/Genotypes.csv")

@@

pfts_wash <- read.csv("./Data From Washington/PFTs.csv")

@@

uofm <- read.csv("./Data from UofM/Moheet_Pre_Post_Trikafta_FinalData_20210914.csv")
analytic_uofm <- subset(uofm, uofm$CFRD.Status == "CFRD with or without fasting hyperglycemia")
analytic_uofm$age <- analytic_uofm$age.at.Trikafta.start

@@

analytic_uofm2$BMI.Value <- analytic_uofm2$bmi
analytic_uofm2_2 <- subset(analytic_uofm2, analytic_uofm2$Encounter....of.Days.POST.Trikafta.start <= 365 &
                             analytic_uofm2$Encounter....of.Days.PRE.Trikafta.Start <= 365)

@@

@@

mycontrols  <- tableby.control(test=FALSE, total=FALSE,
                               numeric.test="kwt", cat.test="chisq",
                               numeric.stats=c("N", "median", "q1q3"),
                               cat.stats=c("countpct"),
                               stats.labels=list(N='Count', median='Median', q1q3='Q1,Q3'))
tab2 <- tableby(prepost ~ n, control=mycontrols, data=a1c7)

@@

#number of values pre/post
#row 1 in table 2
a <- merge(before, after, by = "CFF.ID", all.y = T)

@@

@@

#test this

time <- merge(before_max,after_max,by='CFF.ID',all.y=T)

@@

@@

time$diff_a1c <- as.numeric(time$Hgb.A1C.x) - as.numeric(time$Hgb.A1C.y)

@@

@@

@@

@@

tab2 <- tableby(time~Weight+ bmiz + ppFEV1+ppFVC, data=timing)
timing2 <- merge(weigh_before1,weigh_after1, by = "MRN", all.y=T)

@@

tab2b<- tableby(prepost~ppFVC + ppFEV1 + bmipct + Weight + BMI.Value, 
                data=bmidat4[bmidat4$CFF.ID %in% time[!is.na(time$prepost.x),]$CFF.ID,])
tab2b<- tableby(prepost~ppFVC + ppFEV1 + bmipct + Weight + BMI.Value, 
                data=bmidat4[bmidat4$CFF.ID %in% a$CFF.ID,])

@@

@@

@@

@@

tab3 <- tableby(time~ average_sensor
                + min_sensor
                + max_sensor
                + percent_time_over_120
                + percent_time_over_140
                + percent_time_over_200
                + avg_excur_over_140_per_day
                + avg_excur_over_200_per_day
                + percent_time_under_60
                + percent_time_under_70
                + average_auc_per_day
                + standard_deviation
                + r_mage, data=cgm0_small, control=mycontrols)
tab3 <- tableby(~average_sensor
                + min_sensor
                + max_sensor
                + percent_time_over_120
                + percent_time_over_140
                + percent_time_over_200
                + avg_excur_over_140_per_day
                + avg_excur_over_200_per_day
                + percent_time_under_60
                + percent_time_under_70
                + average_auc_per_day
                + standard_deviation
                + r_mage, data=cgm0[cgm0$time == "post",]
                , control=mycontrols)

@@

@@

tab1 <- tableby(~age+bmipct + Weight + Sex + ppFEV1 + ppFVC  +
                  G.tube.in.past.12.months + Pancreatic.Status +
                  genoRisk + location+BMI.Value + age_category, 
                data=analytic_cm[analytic_cm$CFF.ID %in% cgm0_small$ID,])
summary(tab1)
```
